---
output: html_document
---
Week 2 of Reproducible Research
===============================

```{r setoptions, echo=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, results = "hide")
```

```{r computetime, echo=FALSE}
time <- format(Sys.time(), "%A, %d %B %Y, %X", usetz = TRUE)
```

Generated at `r time`

Let's play with some R Markdown, shan't we.

First, we load the dataset library that comes with R.

```{r results = "hide"}
library(datasets)
```

Then load a dataset of airquality out of there and print out a summary
```{r echo=TRUE}
data(airquality)
summary(airquality)
```

And now we'll plot some of that data

```{r plotAirquality, echo = FALSE}
plot(airquality)
```

Add up a regression model of ozone on wind, solar radiation and temperature

```{r fitmodel}
library(stats)

fit <- lm(Ozone ~ Wind + Solar.R + Temp, data = airquality)
summary(fit)
```

Here's a table of regression coefficients.

```{r showtable, results="asis"}
library(xtable)

xt <- xtable(summary(fit))
print(xt, type = "html")
```


And here's a plot for it

```{r}
plot(fit)
```




## Some more playing around

1. Simulate some data
```{r simulatedata, echo=TRUE, cache=TRUE}
x <- rnorm(100); y <- x + rnorm(100, sd = 0.5)
```

2. Plot a scatterplot for it
```{r scatterplot, fig.height=4}
par(mar = c(5, 4, 1, 1), las = 1)
plot(x, y, main = "Simulated Data")
```